\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-15 k-planar.tex
Consistent notation

For any integer $d\ge 3$, a (multi)graph $G$ is \defin{$d$-framed} if it admits a drawing in the plane having a biconnected plane (multi) subgraph $G_0$, whose facial cycles have length at most $d$,  and such that the interior of each edge in $E(G)\setminus E(G_0)$ is contained in the interior of some face of $G_0$.
% \note{DW}{I suggest we replace ``and whose crossing edges are in the interior of these faces'' by ``such that each edge in $E(G)\setminus E(G_0)$ is in the interior of some face of $G_0$. }
The graph $G_0$ is called the \defin{frame} of $G_0$. This definition (for simple graphs) was introduced by \citet{BDGGMR}. Every $d$-framed multigraph can be described by a $(2,\binom{d}{2})$-shortcut system applied to a planar graph. Thus \cref{ShortcutProduct} is applicable. However, for framed graphs we prove the following stronger result, where the treewidth bound on $H$ is best possible.\footnote{A multigraph $G$ is \defin{contained} in a graph $G'$ if the simple graph underlying $G$ is isomorphic to a subgraph of $G'$.}

>>>>

For any integer $d\ge 3$, a (multi)graph $G$ is \defin{$d$-framed} if it admits a drawing in the plane having a biconnected plane spanning (multi) subgraph $G'$, whose facial cycles have length at most $d$,  and such that the interior of each edge in $E(G)\setminus E(G')$ is contained in the interior of some face of $G'$.
% \note{DW}{I suggest we replace ``and whose crossing edges are in the interior of these faces'' by ``such that each edge in $E(G)\setminus E(G_0)$ is in the interior of some face of $G_0$. }
The graph $G'$ is called the \defin{frame} of $G'$. This definition (for simple graphs) was introduced by \citet{BDGGMR}. Every $d$-framed multigraph can be described by a $(2,\binom{d}{2})$-shortcut system applied to a planar graph. Thus \cref{ShortcutProduct} is applicable. However, for framed graphs we prove the following stronger result, where the treewidth bound on $H$ is best possible.\footnote{A multigraph $G$ is \defin{contained} in a graph $G'$ if the simple graph underlying $G$ is isomorphic to a subgraph of $G'$.}
